---
title: "Rsp_SD_Figures"
author: "Logan Edvalson"
date: "2025-11-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Old Figure 1B

```{r}
# CPM graph for Rsp smRNAs
R16_1 <- read.table("smRNA_counts/all_summedbyFam/R16_Iso1_1_R_R1.out_fam")
R16_2 <- read.table("smRNA_counts/all_summedbyFam/R16_Iso1_2_R1.out_fam")
R16_3 <- read.table("smRNA_counts/all_summedbyFam/R16_Iso1_3_R1.out_fam")
R16_4 <- read.table("smRNA_counts/all_summedbyFam/R16cnbw_1_S6_R1_001.out_fam")
R16_5 <- read.table("smRNA_counts/all_summedbyFam/R16cnbw_2_S10_R1_001.out_fam")
R16_6 <- read.table("smRNA_counts/all_summedbyFam/R16cnbw_R1.out_fam")
SDMad_1 <- read.table("smRNA_counts/all_summedbyFam/SDMad_Iso1_1_R1.out_fam")
SDMad_2 <- read.table("smRNA_counts/all_summedbyFam/SDMad_Iso1_2_R1.out_fam")
SDMad_3 <- read.table("smRNA_counts/all_summedbyFam/SDMad_Iso1_3_R1.out_fam")
SDMad_4 <- read.table("smRNA_counts/all_summedbyFam/SDcnbw_1_S5_R1_001.out_fam")
SDMad_5 <- read.table("smRNA_counts/all_summedbyFam/SDcnbw_2_S9_R1_001.out_fam")
SDMad_6 <- read.table("smRNA_counts/all_summedbyFam/SDcnbw_R1.out_fam")
SDRev_1 <- read.table("smRNA_counts/all_summedbyFam/reverseSd_Iso1_1_R1.out_fam")
SDRev_2 <- read.table("smRNA_counts/all_summedbyFam/reverseSd_Iso1_2_R1.out_fam")
SDRev_3 <- read.table("smRNA_counts/all_summedbyFam/reverseSd_Iso1_3_R1.out_fam")
SDRev_4 <- read.table("smRNA_counts/all_summedbyFam/reverseSd_Iso1_1_S18_R1_001.out_fam")
SDRev_5 <- read.table("smRNA_counts/all_summedbyFam/reverseSd_Iso1_2_S4_R1_001.out_fam")
SDRev_6 <- read.table("smRNA_counts/all_summedbyFam/reverseSd_Iso1_3_S5_R1_001.out_fam")
SD5_1 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_1_R1.out_fam")
SD5_2 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_2_R1.out_fam")
SD5_3 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_3_R1.out_fam")
SD5_4 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_1_S14_R1_001.out_fam")
SD5_5 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_2_S15_R1_001.out_fam")
SD5_6 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_3_S16_R1_001.out_fam")

element <- "Rsp"
R16_CPM <- mean(c(extractCPM(R16_1, element), extractCPM(R16_2, element), extractCPM(R16_3, element),extractCPM(R16_4, element),extractCPM(R16_5, element),extractCPM(R16_6, element)))
R16_StD <- sd(c(extractCPM(R16_1, element), extractCPM(R16_2, element), extractCPM(R16_3, element),extractCPM(R16_4, element),extractCPM(R16_5, element),extractCPM(R16_6, element)))
SDMad_CPM <- mean(c(extractCPM(SDMad_1, element), extractCPM(SDMad_2, element), extractCPM(SDMad_3, element), extractCPM(SDMad_4, element), extractCPM(SDMad_5, element), extractCPM(SDMad_6, element)))
SDMad_StD <- sd(c(extractCPM(SDMad_1, element), extractCPM(SDMad_2, element), extractCPM(SDMad_3, element), extractCPM(SDMad_4, element), extractCPM(SDMad_5, element), extractCPM(SDMad_6, element)))
SDRev_CPM <- mean(c(extractCPM(SDRev_1, element), extractCPM(SDRev_2, element), extractCPM(SDRev_3, element), extractCPM(SDRev_4, element), extractCPM(SDRev_5, element), extractCPM(SDRev_6, element)))
SDRev_StD <- sd(c(extractCPM(SDRev_1, element), extractCPM(SDRev_2, element), extractCPM(SDRev_3, element), extractCPM(SDRev_4, element), extractCPM(SDRev_5, element), extractCPM(SDRev_6, element)))
SD5_CPM <- mean(c(extractCPM(SD5_1, element), extractCPM(SD5_2, element), extractCPM(SD5_3, element), extractCPM(SD5_4, element), extractCPM(SD5_5, element), extractCPM(SD5_6, element)))
SD5_StD <- sd(c(extractCPM(SD5_1, element), extractCPM(SD5_2, element), extractCPM(SD5_3, element), extractCPM(SD5_4, element), extractCPM(SD5_5, element), extractCPM(SD5_6, element)))

data <- data.frame(Group = c("R16/Iso1", "SDMad/Iso1", "SDRev/Iso1","SD5/Iso1"), Mean = c(R16_CPM, SDMad_CPM, SDRev_CPM, SD5_CPM), STDev = c(R16_StD, SDMad_StD, SDRev_StD, SD5_StD))

data$Group <- factor(data$Group, levels = c("R16/Iso1", "SDMad/Iso1", "SDRev/Iso1","SD5/Iso1"))

point_Data <- data.frame(Group = rep(c("R16/Iso1", "SDMad/Iso1", "SDRev/Iso1", "SD5/Iso1"), each = 6), 
                         CPM = c(
                           extractCPM(R16_1, element), extractCPM(R16_2, element), extractCPM(R16_3, element),extractCPM(R16_4, element),extractCPM(R16_5, element),extractCPM(R16_6, element),
                           extractCPM(SDMad_1, element), extractCPM(SDMad_2, element), extractCPM(SDMad_3, element), extractCPM(SDMad_4, element), extractCPM(SDMad_5, element), extractCPM(SDMad_6, element),
                           extractCPM(SDRev_1, element), extractCPM(SDRev_2, element), extractCPM(SDRev_3, element), extractCPM(SDRev_4, element), extractCPM(SDRev_5, element), extractCPM(SDRev_6, element),
                           extractCPM(SD5_1, element), extractCPM(SD5_2, element), extractCPM(SD5_3, element), extractCPM(SD5_4, element), extractCPM(SD5_5, element), extractCPM(SD5_6, element)))

point_Data$Group <- factor(point_Data$Group, levels = c("R16/Iso1","SDMad/Iso1","SDRev/Iso1","SD5/Iso1"))

upper <- data$Mean + data$STDev
lower <- data$Mean - data$STDev

ggplot(data, aes(y = Mean, fill = Group)) +
    geom_bar(aes(x = Group, y = Mean), stat = "identity", width = 0.6) +
    geom_point(data = point_Data,
           aes(x = Group, y = CPM),
           position = position_jitter(width = 0.08),
           size = 3,
           color = "black") +
    scale_fill_manual(values=c("gray", "seagreen", "darkgoldenrod2", "dodgerblue3")) +
    geom_errorbar(aes(x = Group, ymin = lower, ymax = upper), width = 0.1) +
    labs(x = NULL, y = "Mean CPM ± StDev") +
    theme_classic() +
    theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

TukeyHSD(aov(CPM ~ Group, data = point_Data))

ggsave("smRNA_CPMPlot_Iso1.pdf", width = 6, height = 6, units = c("in"), bg = "transparent")
```

# NEW FIG 1B
```{r}
FC_Points_SDMad <- normCounts_SDMad_R16_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SDMad_R16_Iso1_smRNA)) == TRUE,]
FC_Points_SDMad <- data.frame(Group = c(rep("R16/Iso1(MAD)", 6), rep("SDMad/Iso1", 6)),
                              Count = as.numeric(FC_Points_SDMad[1,]))

FC_Points_SDRev <- normCounts_SDMadRev_R16_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SDMadRev_R16_Iso1_smRNA)) == TRUE,]
FC_Points_SDRev <- data.frame(Group = c(rep("SDRev/Iso1", 6), rep("R16/Iso1(REV)", 5)),
                              Count = as.numeric(FC_Points_SDRev[1,]))

FC_Points_SD5 <- normCounts_SD5_R16_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SD5_R16_Iso1_smRNA)) == TRUE,]
FC_Points_SD5 <- data.frame(Group = c(rep("R16/Iso1(SD5)", 3), rep("SD5/Iso1", 3)),
                              Count = as.numeric(FC_Points_SD5[1,]))


points <- bind_rows(
  FC_Points_SDMad,
  FC_Points_SDRev,
  FC_Points_SD5
)

points$Pair <- rep(c("SDMad","SDRev","SD5"),
                   times = c(nrow(FC_Points_SDMad),
                             nrow(FC_Points_SDRev),
                             nrow(FC_Points_SD5)))

points$Pair <- factor(points$Pair, levels=c("SDMad","SDRev","SD5"))
points$Group <- factor(points$Group,
                       levels=c("R16/Iso1(MAD)","SDMad/Iso1",
                                "R16/Iso1(REV)","SDRev/Iso1",
                                "R16/Iso1(SD5)","SD5/Iso1"))

summary_df <- points |>
  dplyr::group_by(Pair, Group) |>
  dplyr::summarise(
    Mean = mean(Count),
    SD = sd(Count),
    .groups="drop"
  )

summary_df$Group <- factor(summary_df$Group,
                           levels = c("R16/Iso1(MAD)","SDMad/Iso1",
                                      "R16/Iso1(REV)","SDRev/Iso1",
                                      "R16/Iso1(SD5)","SD5/Iso1"))

points$Group <- factor(points$Group,
                       levels = levels(summary_df$Group))

summary_Mad <- summary_df[grepl("Mad", summary_df$Pair) == TRUE, ]
summary_Rev <- summary_df[grepl("Rev", summary_df$Pair) == TRUE, ]
summary_5 <- summary_df[grepl("SD5", summary_df$Pair) == TRUE, ]

points_Mad <- points[grepl("Mad", points$Pair) == TRUE, ]
points_Rev <- points[grepl("Rev", points$Pair) == TRUE, ]
points_5 <- points[grepl("SD5", points$Pair) == TRUE, ]

ggplot(summary_Mad, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_Mad,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("gray","seagreen")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("smRNA_CPMPlot_SDMad_Iso1.pdf", width = 8, height = 6, units = c("in"), bg = "transparent")

ggplot(summary_Rev, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_Rev,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("gray","darkgoldenrod2")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("smRNA_CPMPlot_SDRev_Iso1.pdf", width = 8, height = 6, units = c("in"), bg = "transparent")

ggplot(summary_5, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_5,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("gray","dodgerblue3")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("smRNA_CPMPlot_SD5_Iso1.pdf", width = 8, height = 6, units = c("in"), bg = "transparent")
```
# Alternate Figure 1B
```{r}
FC_Points_SDMad <- normCounts_SDMad_R16_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SDMad_R16_Iso1_smRNA)) == TRUE,]
FC_Points_SDMad <- data.frame(Group = c(rep("R16/Iso1", 6), rep("SDMad/Iso1", 6)),
                              Count = as.numeric(FC_Points_SDMad[1,]))

average_FC_SDMad <- -(1 - (mean(c(FC_Points_SDMad[FC_Points_SDMad$Group == "SDMad/Iso1",2])) / mean(c(FC_Points_SDMad[FC_Points_SDMad$Group == "R16/Iso1",2]))))

FC_Points_SDRev <- normCounts_SDMadRev_R16_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SDMadRev_R16_Iso1_smRNA)) == TRUE,]
FC_Points_SDRev <- data.frame(Group = c(rep("SDRev/Iso1", 6), rep("R16/Iso1", 5)),
                              Count = as.numeric(FC_Points_SDRev[1,]))

average_FC_SDRev <- -(1 - (mean(c(FC_Points_SDRev[FC_Points_SDRev$Group == "SDRev/Iso1",2])) / mean(c(FC_Points_SDRev[FC_Points_SDRev$Group == "R16/Iso1",2]))))

FC_Points_SD5 <- normCounts_SD5_R16_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SD5_R16_Iso1_smRNA)) == TRUE,]
FC_Points_SD5 <- data.frame(Group = c(rep("R16/Iso1", 3), rep("SD5/Iso1", 3)),
                              Count = as.numeric(FC_Points_SD5[1,]))

average_FC_SD5 <- -(1 - (mean(c(FC_Points_SD5[FC_Points_SD5$Group == "SD5/Iso1",2])) / mean(c(FC_Points_SD5[FC_Points_SD5$Group == "R16/Iso1",2]))))

Means <- c(average_FC_SDMad, average_FC_SDRev, average_FC_SD5)

StD_SDMad <- sd(-(1 - (c(FC_Points_SDMad[FC_Points_SDMad$Group == "SDMad/Iso1",2])) / mean(c(FC_Points_SDMad[FC_Points_SDMad$Group == "R16/Iso1",2]))))
StD_SDRev <- sd(-(1 - (c(FC_Points_SDRev[FC_Points_SDRev$Group == "SDRev/Iso1",2])) / mean(c(FC_Points_SDRev[FC_Points_SDRev$Group == "R16/Iso1",2]))))
StD_SD5 <- sd(-(1 - (c(FC_Points_SD5[FC_Points_SD5$Group == "SD5/Iso1",2])) / mean(c(FC_Points_SD5[FC_Points_SD5$Group == "R16/Iso1",2]))))

StDs <- c(StD_SDMad, StD_SDRev, StD_SD5)

data <- data.frame(Group = c("SDMad/Iso1", "SDRev/Iso1", "SD5/Iso1"), Mean = Means, STDev = StDs)

data$Group <- factor(data$Group, levels = c("SDMad/Iso1", "SDRev/Iso1","SD5/Iso1"))

upper <- data$Mean + data$STDev
lower <- data$Mean - data$STDev

ggplot(data, aes(y = Mean, fill = Group)) +
    geom_bar(aes(x = Group, y = Mean), stat = "identity", width = 0.6) +
    scale_fill_manual(values=c("seagreen", "darkgoldenrod2", "dodgerblue3")) +
    geom_errorbar(aes(x = Group, ymin = lower, ymax = upper), width = 0.1) +
    labs(x = NULL, y = "% Change ± StDev") +
    theme_classic() +
    geom_hline(yintercept = 0) +
    theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("smRNA_CPMPlot.pdf", width = 10, height = 6, units = c("in"), bg = "transparent")
```

# Figure 1C

```{r}
piRNALoci <- c("Rsp", "1pt688","piRNA_cluster_38C2", "piRNA_cluster_38C1", "piRNA_cluster_flamenco", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_42AB")
piRNALoci <- factor(piRNALoci, levels = c("Rsp", "1pt688","piRNA_cluster_38C1","piRNA_cluster_38C2", "piRNA_cluster_42AB", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_flamenco"))
gene_data <- data.frame(
  Gene = piRNALoci, 
  logFC_SDMad = SDMad_R16_smRNA_Iso1$LogFC[match(piRNALoci, SDMad_R16_smRNA_Iso1$Name)], logFC_SDRev = SDMadRev_R16_smRNA_Iso1$LogFC[match(piRNALoci, SDMadRev_R16_smRNA_Iso1$Name)], logFC_SD5 = SD5_R16_smRNA_Iso1$LogFC[match(piRNALoci, SD5_R16_smRNA_Iso1$Name)], 
  p.Adj_SDMad = SDMad_R16_smRNA_Iso1$p.Adj[match(piRNALoci, SDMad_R16_smRNA_Iso1$Name)], p.Adj_SDRev = SDMadRev_R16_smRNA_Iso1$p.Adj[match(piRNALoci, SDMadRev_R16_smRNA_Iso1$Name)], p.Adj_SD5 = SD5_R16_smRNA_Iso1$p.Adj[match(piRNALoci, SD5_R16_smRNA_Iso1$Name)])

df_long <- gene_data %>%
  pivot_longer(cols = starts_with("logFC"),
               names_to = "Condition",
               values_to = "logFC") %>%
  mutate(Condition = sub("logFC_", "", Condition)) %>%
  left_join(
    gene_data %>%
      pivot_longer(cols = starts_with("p.Adj"),
                   names_to = "Condition_p",
                   values_to = "p.Adj") %>%
      mutate(Condition = sub("p.Adj_", "", Condition_p)) %>%
      dplyr::select(Gene, Condition, p.Adj),
    by = c("Gene", "Condition")
  ) %>%
  mutate(sig = case_when(p.Adj <= 0.001 ~ "***",p.Adj <= 0.01  ~ "**",p.Adj <= 0.05  ~ "*",TRUE ~ ""))



ggplot(df_long, aes(x = Gene, y = Condition, fill = logFC)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sig), color = "black", size = 5) +
  scale_fill_gradient2(low = "dodgerblue3", mid = "white", high = "red2", midpoint = 0, name = "Log2FC") +
  scale_x_discrete(labels = c(
    "Rsp" = "Rsp",
    "1pt688" = "1.688",
    "piRNA_cluster_38C2" = "38C2",
    "piRNA_cluster_38C1" = "38C1",
    "piRNA_cluster_flamenco" = "Flamenco",
    "piRNA_cluster_80F" = "80F",
    "piRNA_cluster_20A" = "20A",
    "piRNA_cluster_42AB" = "42AB"
  )) +
  scale_y_discrete(labels = c(
    "SDMad" = "SDMad/Iso1",
    "SDRev" = "SDRev/Iso1",
    "SD5" = "SD5/Iso1"
  )) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title = element_blank(), legend.text = element_text(size = 15), legend.title = element_text(size = 15))

ggsave("smRNA_HeatPlot_Iso1.pdf", width = 10, height = 3, bg = "transparent")
```

#Figure 2A

```{r}
SDMad_R16_DEList <- SDMad_R16_totRNA_Gla[SDMad_R16_totRNA_Gla$p.Adj <= 0.05,]
SDMad_R16_DEList_Names <- SDMad_R16_DEList$Name

SD5_R16_DEList <- SD5_R16_totRNA_Gla[SD5_R16_totRNA_Gla$p.Adj <= 0.05,]
SD5_R16_DEList_Names <- SD5_R16_DEList$Name

individualization_GeneSet <- read.table("Individualization_GeneSet.txt")
colnames(individualization_GeneSet) <- c("SYMBOL", "FLYBASE")

SDMad_data <- SDMad_R16_totRNA_Gla[SDMad_R16_totRNA_Gla$Name %in% individualization_GeneSet$FLYBASE,]
SD5_data <- SD5_R16_totRNA_Gla[SD5_R16_totRNA_Gla$Name %in% individualization_GeneSet$FLYBASE,]
merged_Data_Gla <- merge(SDMad_data, SD5_data, by = "Name")

indData <- na.omit(data.frame(Gene = merged_Data_Gla$SYMBOL.x, logFC_SDMad = merged_Data_Gla$LogFC.x, p.Adj_SDMad = merged_Data_Gla$p.Adj.x, logFC_SD5 = merged_Data_Gla$LogFC.y, p.Adj_SD5 = merged_Data_Gla$p.Adj.y))

write_tsv(indData, "supplementalTables/individualizationTable_Gla.tsv")

df_long_indData <- indData %>%
  pivot_longer(cols = starts_with("logFC"),
               names_to = "Condition",
               values_to = "logFC") %>%
  mutate(Condition = sub("logFC_", "", Condition)) %>%
  left_join(
    indData %>%
      pivot_longer(cols = starts_with("p.Adj"),
                   names_to = "Condition_p",
                   values_to = "p.Adj") %>%
      mutate(Condition = sub("p.Adj_", "", Condition_p)) %>%
      dplyr::select(Gene, Condition, p.Adj),
    by = c("Gene", "Condition")
  ) %>%
  mutate(sig = case_when(p.Adj <= 0.001 ~ "***",p.Adj <= 0.01  ~ "**",p.Adj <= 0.05  ~ "*",TRUE ~ ""))

ggplot(df_long_indData, aes(x = Gene, y = Condition, fill = logFC)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "dodgerblue3", mid = "white", high = "red2", midpoint = 0, name = "log2FC") +
  theme_minimal() +
  geom_text(aes(label = sig, angle = 90), color = "black", size = 10, vjust = 0.75) +
  theme(axis.text.x = element_text(size = 20, angle = 45, hjust = 1, face = "italic"), axis.text.y = element_text(size = 30), axis.title = element_blank(), legend.text = element_text(size = 40), legend.title = element_text(size = 40), legend.key.size = unit(0.5, "in")) +
  scale_y_discrete(labels = c("SDMad" = "SDMad/Gla", "SD5" = "SD5/Gla"))

ggsave("individualization_HeatPlot.pdf", width = 25, height = 6, bg = "transparent")
```

#Figure 2B

```{r}
plotData <- bind_rows(SDMadComp, SD5Comp)

plotData <- plotData %>%
  mutate(sig = case_when(
    padj <= 0.001 ~ "***",
    padj <= 0.01  ~ "**",
    padj <= 0.05  ~ "*",
    TRUE ~ ""
  ))

write_tsv(plotData, "supplementalTables/TableS3.tsv")

ggplot(plotData, aes(x = condition, y = Module, fill = difference)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sig), color = "black", size = 10) +
  scale_fill_gradient2(
    low = "dodgerblue3",
    mid = "white",
    high = "red2",
    midpoint = 0,
    name = "Difference"
  ) +
  theme_minimal(base_size = 16) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 30),
    axis.text.y = element_text(size = 20),
    axis.title = element_blank(),
    plot.title = element_text(hjust = 0.5),
    legend.justification = c("right", "center"),
    legend.text = element_text(size = 20),
    legend.title = element_text(size = 20)) +
  scale_y_discrete(labels = c(
    "MEyellow" = "Module A",
    "MEturquoise" = "Module B",
    "MEred" = "Module C",
    "MEpink" = "Module D",
    "MEgrey" = "Module E",
    "MEgreen" = "Module F",
    "MEbrown" = "Module G",
    "MEblue" = "Module H",
    "MEblack" = "Module I"
    )) +
  scale_x_discrete((labels = c(
    "SDMad" = "SDMad",
    "SD5" = "SD5"
  )))

ggsave("WGCNA_HeatPlot.pdf", width = 6, height = 15, bg = "transparent")

B_DotPlotData <- read_csv("PANGEA_Results/Module_B_PANGEA.csv")
G_DotPlotData <- read_csv("PANGEA_Results/Module_G_PANGEA.csv")

A_DotPlotData <- read_csv("PANGEA_Results/Module_A_PANGEA.csv")
H_DotPlotData <- read_csv("PANGEA_Results/Module_H_PANGEA.csv")

C_DotPlotData <- read_csv("PANGEA_Results/Module_C_PANGEA.csv")
F_DotPlotData <- read_csv("PANGEA_Results/Module_F_PANGEA.csv")

WGCNA_PangeaDotPlot(H_DotPlotData, dotplotprefix = "Module_H", numSets = 20, plotWidth = 13, plotHeight = 24)
WGCNA_PangeaDotPlot(B_DotPlotData, dotplotprefix = "Module_B", numSets = 20, plotWidth = 16, plotHeight = 24)

WGCNA_PangeaDotPlot(G_DotPlotData, dotplotprefix = "Module_G")
WGCNA_PangeaDotPlot(A_DotPlotData, dotplotprefix = "Module_A")


WGCNA_PangeaDotPlot(C_DotPlotData, dotplotprefix = "Module_C")
WGCNA_PangeaDotPlot(F_DotPlotData, dotplotprefix = "Module_F")
```

#Figure 3B

```{r}
#Testis kipferl qPCR
data <- data.frame(Group = c("Rsp", "359bp"), Mean = c(1.94, 2.85), STDev = c(0.82, 1.63), pVal = c("P=0.038", "P=0.064"))

 upper <- data$Mean + data$STDev
  lower <- data$Mean - data$STDev
  
  data$Genotype <- factor(data$Group, levels = data$Group)
  
  ggplot(data, aes(y = Mean, fill = Group)) +
    geom_bar(aes(x = Group, y = Mean), stat = "identity", width = 0.6) +
    scale_fill_manual(values=c("chocolate4", "royalblue3")) +
    geom_errorbar(aes(x = Group, ymin = lower, ymax = upper), width = 0.1) +
    geom_text(aes(x = Group, label = pVal, y = upper + 0.5), size = 5) +
    geom_hline(yintercept=1, linetype='dashed', col = 'red', size = 1) +
    labs(y = "Fold Change ± StDv") +
    theme_minimal() +
    theme(legend.position = "none", axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 18), panel.grid = element_blank())
  
ggsave("KipKO_Testis_qPCR.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")

# Ovary kipferl qPCR
data <- data.frame(Group = c("Rsp", "359bp"), Mean = c(4.87, 8.26), STDev = c(1.98, 2.3), pVal = c("P=0.03", "P=0.008"))

 upper <- data$Mean + data$STDev
  lower <- data$Mean - data$STDev
  
  data$Genotype <- factor(data$Group, levels = data$Group)
  
  ggplot(data, aes(y = Mean, fill = Group)) +
    geom_bar(aes(x = Group, y = Mean), stat = "identity", width = 0.6) +
    scale_fill_manual(values=c("chocolate4", "royalblue3")) +
    geom_errorbar(aes(x = Group, ymin = lower, ymax = upper), width = 0.1) +
    geom_text(aes(x = Group, label = pVal, y = upper + 0.5), size = 5) +
    geom_hline(yintercept=1, linetype='dashed', col = 'red', size = 1) +
    labs(y = "Fold Change ± StDv") +
    theme_minimal() +
    theme(legend.position = "none", axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 18), panel.grid = element_blank())
  
ggsave("KipKO_Ovary_qPCR.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")
```

#Figure 3C

```{r}
# KipKD K values: Iso1
data <- data.frame(
  White = c(0.992, 0.987, 0.995, 0.985, 0.981, 0.942, 0.989, 1, 0.983),
  Kip = c(0.847, 0.928, 0.837, 0.858, 0.896, 0.943, 0.919, NA, NA)
)

long_data <- pivot_longer(data, cols = everything(), names_to = "shRNA", values_to = "K_Val")

long_data$shRNA <- factor(long_data$shRNA, levels = c("White", "Kip"))

ggplot(long_data, aes(x = shRNA, y = K_Val, fill = shRNA)) +
  geom_boxplot(outlier.shape = 21, outlier.fill = "white", outlier.color = "black") +
  scale_x_discrete(labels = c("White" = "White shRNA",
                              "Kip" = "Kipferl shRNA")) +
  scale_fill_manual(values = c("darkgrey", "seagreen")) +
  scale_y_continuous(limits = c(0.5,1)) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title.x = element_blank())

ggsave("Iso1_Bam_Kvalue.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")
```

#Figure 3D

```{r}
# KipKO K values: Iso1
data <- data.frame(
  Homozygote = c(0.81,0.83,0.92,0.74,0.83,0.76,0.81,0.85,0.79,NA,NA,NA,NA),
  Heterozygote = c(1,0.99,0.99,0.99,0.99,0.99,0.78,0.99,0.99,1,1,0.97,1)
)

long_data <- pivot_longer(data, cols = everything(), names_to = "genotype", values_to = "K_Val")

long_data$genotype <- factor(long_data$genotype, levels = c("Heterozygote", "Homozygote"))

ggplot(long_data, aes(x = genotype, y = K_Val, fill = genotype)) +
  geom_boxplot(outlier.shape = 21, outlier.fill = "white", outlier.color = "black") +
  scale_fill_manual(values = c("darkgrey", "seagreen")) +
  scale_y_continuous(limits = c(0.5,1)) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title.x = element_blank())

ggsave("SDMad_Iso1_KipKO_Kvalue.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")


data <- data.frame(
  Homozygote = c(0.951456311,0.906403941,0.955223881,0.917355372,0.968992248,0.985714286,0.986111111,0.824175824),
  Heterozygote = c(1,0.996212121,1,1)
)

long_data <- pivot_longer(data, cols = everything(), names_to = "genotype", values_to = "K_Val")

long_data$genotype <- factor(long_data$genotype, levels = c("Heterozygote", "Homozygote"))

ggplot(long_data, aes(x = genotype, y = K_Val, fill = genotype)) +
  geom_boxplot(outlier.shape = 21, outlier.fill = "white", outlier.color = "black") +
  scale_fill_manual(values = c("darkgrey", "dodgerblue3")) +
  scale_y_continuous(limits = c(0.5,1)) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title.x = element_blank())

ggsave("SD5_Iso1_KipKO_Kvalue.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")
```

#Figure 4B

```{r}
piRNALoci <- c("Rsp", "1pt688","piRNA_cluster_38C2", "piRNA_cluster_38C1", "piRNA_cluster_flamenco", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_42AB")
piRNALoci <- factor(piRNALoci, levels = c("Rsp", "1pt688","piRNA_cluster_38C1","piRNA_cluster_38C2", "piRNA_cluster_42AB", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_flamenco"))
gene_data <- data.frame(
  Gene = piRNALoci, 
  logFC_SDMad = SDMad_RspOE_SDMad_smRNA_Iso1$LogFC[match(piRNALoci, SDMad_RspOE_SDMad_smRNA_Iso1$Name)], 
  logFC_SD5 = SD5_RspOE_SD5_smRNA_Iso1$LogFC[match(piRNALoci, SD5_RspOE_SD5_smRNA_Iso1$Name)], 
  #logFC_SDMad_dsRed = SDMad_RspOE_dsRed_SDMad_smRNA_Iso1$LogFC[match(piRNALoci, SDMad_RspOE_dsRed_SDMad_smRNA_Iso1$Name)],
  #logFC_SD5_dsRed = SD5_RspOE_dsRed_SD5_smRNA_Iso1$LogFC[match(piRNALoci, SD5_RspOE_dsRed_SD5_smRNA_Iso1$Name)],
  p.Adj_SDMad = SDMad_RspOE_SDMad_smRNA_Iso1$p.Adj[match(piRNALoci, SDMad_RspOE_SDMad_smRNA_Iso1$Name)], 
  p.Adj_SD5 = SD5_RspOE_SD5_smRNA_Iso1$p.Adj[match(piRNALoci, SD5_RspOE_SD5_smRNA_Iso1$Name)])
  #p.Adj_SDMad_dsRed = SDMad_RspOE_dsRed_SDMad_smRNA_Iso1$p.Adj[match(piRNALoci, SDMad_RspOE_dsRed_SDMad_smRNA_Iso1$Name)], 
  #p.Adj_SD5_dsRed = SD5_RspOE_dsRed_SD5_smRNA_Iso1$p.Adj[match(piRNALoci, SD5_RspOE_dsRed_SD5_smRNA_Iso1$Name)])


df_long <- gene_data %>%
  pivot_longer(cols = starts_with("logFC"),
               names_to = "Condition",
               values_to = "logFC") %>%
  mutate(Condition = sub("logFC_", "", Condition)) %>%
  left_join(
    gene_data %>%
      pivot_longer(cols = starts_with("p.Adj"),
                   names_to = "Condition_p",
                   values_to = "p.Adj") %>%
      mutate(Condition = sub("p.Adj_", "", Condition_p)) %>%
      dplyr::select(Gene, Condition, p.Adj),
    by = c("Gene", "Condition")
  ) %>%
  mutate(sig = case_when(p.Adj <= 0.001 ~ "***",p.Adj <= 0.01  ~ "**",p.Adj <= 0.05  ~ "*",TRUE ~ ""))

ggplot(df_long, aes(x = Gene, y = Condition, fill = logFC)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sig), color = "black", size = 8) +
  scale_fill_gradient2(low = "dodgerblue3", mid = "white", high = "red2", midpoint = 0, name = "log2FC") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 20, vjust = 1, face = "italic"), axis.text.y = element_text(size = 15), axis.title = element_blank(), legend.text = element_text(size = 15), legend.title = element_text(size = 20)) +
  scale_x_discrete(labels = c(
    "Rsp" = "Rsp",
    "1pt688" = "1.688",
    "piRNA_cluster_38C2" = "38C2",
    "piRNA_cluster_38C1" = "38C1",
    "piRNA_cluster_flamenco" = "Flamenco",
    "piRNA_cluster_80F" = "80F",
    "piRNA_cluster_20A" = "20A",
    "piRNA_cluster_42AB" = "42AB"
  ))  

ggsave("smRNA_HeatPlot_RspOE.pdf", width = 10, height = 5, bg = "transparent")
```

#Old Figure 4C

```{r}
SDMad_1 <- read.table("smRNA_counts/all_summedbyFam/SDMad_Iso1_new_1_R1.out_fam")
SDMad_2 <- read.table("smRNA_counts/all_summedbyFam/SDMad_Iso1_new_2_R1.out_fam")
SDMad_3 <- read.table("smRNA_counts/all_summedbyFam/SDMad_Iso1_new_3_R1.out_fam")
SDMadRspOE_1 <- read.table("smRNA_counts/all_summedbyFam/SDMad_RspOE_new_1_R1.out_fam")
SDMadRspOE_2 <- read.table("smRNA_counts/all_summedbyFam/SDMad_RspOE_new_2_R1.out_fam")
SDMadRspOE_3 <- read.table("smRNA_counts/all_summedbyFam/SDMad_RspOE_new_3_R1.out_fam")
SD5_1 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_new_1_R1.out_fam")
SD5_2 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_new_2_R1.out_fam")
SD5_3 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_new_3_R1.out_fam")
SD5RspOE_1 <- read.table("smRNA_counts/all_summedbyFam/SD5_RspOE_new_1_R1.out_fam")
SD5RspOE_2 <- read.table("smRNA_counts/all_summedbyFam/SD5_RspOE_new_2_R1.out_fam")
SD5RspOE_3 <- read.table("smRNA_counts/all_summedbyFam/SD5_RspOE_new_3_R_R1.out_fam")

element <- "Rsp"
SDMad_CPM <- mean(extractCPM(SDMad_1, element), extractCPM(SDMad_2, element), extractCPM(SDMad_3, element))
SDMad_StD <- sd(c(extractCPM(SDMad_1, element), extractCPM(SDMad_2, element), extractCPM(SDMad_3, element)))
SDMadRspOE_CPM <- mean(extractCPM(SDMadRspOE_1, element), extractCPM(SDMadRspOE_2, element), extractCPM(SDMadRspOE_3, element))
SDMadRspOE_StD <- sd(c(extractCPM(SDMadRspOE_1, element), extractCPM(SDMadRspOE_2, element), extractCPM(SDMadRspOE_3, element)))
SD5_CPM <- mean(extractCPM(SD5_1, element), extractCPM(SD5_2, element), extractCPM(SD5_3, element))
SD5_StD <- sd(c(extractCPM(SD5_1, element), extractCPM(SD5_2, element), extractCPM(SD5_3, element)))
SD5RspOE_CPM <- mean(extractCPM(SD5RspOE_1, element), extractCPM(SD5RspOE_2, element), extractCPM(SD5RspOE_3, element))
SD5RspOE_StD <- sd(c(extractCPM(SD5RspOE_1, element), extractCPM(SD5RspOE_2, element), extractCPM(SD5RspOE_3, element)))

# RspOE Expression Plot
df_wide <- data.frame(
  Condition = c("SDMad/Iso1 vs SDMad/RspOE", "SD5/Iso1 vs SD5/RspOE"),
  Control = c(SDMad_CPM, SD5_CPM),
  Treatment = c(SDMadRspOE_CPM, SD5RspOE_CPM),
  StDevC = c(SDMad_StD, SD5_StD),
  StDevT = c(SDMadRspOE_StD, SD5RspOE_StD)
)

df_wide$Condition <- factor(df_wide$Condition, levels = c("SDMad/Iso1 vs SDMad/RspOE", "SD5/Iso1 vs SD5/RspOE"))

df_long <- df_wide %>%
  dplyr::select(Condition, Control, Treatment, StDevC, StDevT) %>%
  pivot_longer(
    cols = c(Control, Treatment),
    names_to = "Group",
    values_to = "Value"
  ) %>%
  mutate(StDev = ifelse(Group == "Control", StDevC, StDevT)) %>%
  dplyr::select(Condition, Group, Value, StDev)

df_long$BarColor <- c("seagreen", "seagreen3", "dodgerblue3", "cornflowerblue")
df_long$BarColor <- factor(df_long$BarColor, levels = c("seagreen", "seagreen3", "dodgerblue3", "cornflowerblue"))

ggplot(df_long, aes(x = Condition, y = Value, fill = BarColor)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8),
           width = 0.8, color = "black") +
  geom_errorbar(
    aes(ymin = Value - StDev, ymax = Value + StDev, group = BarColor),
    position = position_dodge(width = 0.8),
    width = 0.2
  ) +
  scale_fill_identity() +  # uses exact colors in BarColor
  labs(x = "", y = expression(italic("Rsp") * " CPM")) +
  theme_minimal() +
  theme(axis.title.y = element_text(size = 30),
        axis.text.y = element_text(size = 26),
        legend.position = "none", panel.grid = element_blank())

ggsave("rspOE_smRNACounts_DESeq2.pdf", width = 10, height = 6, bg = "transparent")
```

# New Figure 4C

```{r}
OE_Points_SDMad <- normCounts_SDMad_RspOE_SDMad_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SDMad_RspOE_SDMad_Iso1_smRNA)) == TRUE,]
OE_Points_SDMad <- data.frame(Group = c(rep("SDMad/Iso1", 3), rep("SDMad/RspOE", 3)),
                              Count = as.numeric(OE_Points_SDMad[1,]))

OE_Points_SD5 <- normCounts_SD5_RspOE_SD5_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SD5_RspOE_SD5_Iso1_smRNA)) == TRUE,]
OE_Points_SD5 <- data.frame(Group = c(rep("SD5/Iso1", 3), rep("SD5/RspOE", 3)),
                              Count = as.numeric(OE_Points_SD5[1,]))


points <- bind_rows(
  OE_Points_SDMad,
  OE_Points_SD5
)

points$Pair <- rep(c("SDMad","SD5"),
                   times = c(nrow(OE_Points_SDMad),
                             nrow(OE_Points_SD5)))

points$Pair <- factor(points$Pair, levels=c("SDMad","SD5"))
points$Group <- factor(points$Group,
                       levels=c("SDMad/Iso1","SDMad/RspOE",
                                "SD5/Iso1","SD5/RspOE"))

summary_df <- points |>
  dplyr::group_by(Pair, Group) |>
  dplyr::summarise(
    Mean = mean(Count),
    SD = sd(Count),
    .groups="drop"
  )

summary_df$Group <- factor(summary_df$Group,
                           levels = c("SDMad/Iso1","SDMad/RspOE",
                                      "SD5/Iso1","SD5/RspOE"))

points$Group <- factor(points$Group,
                       levels = levels(summary_df$Group))

summary_Mad <- summary_df[grepl("Mad", summary_df$Pair) == TRUE, ]
summary_5 <- summary_df[grepl("SD5", summary_df$Pair) == TRUE, ]

points_Mad <- points[grepl("Mad", points$Pair) == TRUE, ]
points_5 <- points[grepl("SD5", points$Pair) == TRUE, ]

ggplot(summary_Mad, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_Mad,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("seagreen","seagreen3")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("rspOE_smRNACounts_SDMad_DESeq2.pdf", width = 6, height = 6, bg = "transparent")

ggplot(summary_5, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_5,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("dodgerblue3","cornflowerblue")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("rspOE_smRNACounts_SD5_DESeq2.pdf", width = 6, height = 6, bg = "transparent")
```

# Figure 4D

```{r}
#SDMad, III from cyo/gla
data <- data.frame(
  kValues = c(0.820809249,0.845070423,0.75,0.903225806,0.726190476,0.834920635,0.909465021,0.888586957,
            0.661764706,0.731225296,0.71031746,0.668257757,0.743801653,0.721854305,0.75,0.715083799,0.691729323),
  Genotype = c(rep("Iso1", 8), rep("RspOE", 9)))
data$Genotype <= factor(data$Genotype, levels = c("Iso1", "RspOE"))

ggplot(data, aes(x = Genotype, y = kValues, fill = Genotype)) +
  geom_boxplot(position = position_dodge(0.7), width = 0.65) +
  labs(x = NULL, y = expression("Prop. of " * italic("SD") * " Progeny")) +
  scale_fill_manual(values = c("seagreen", "springgreen2")) +
  ylim(c(0.5,1)) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20, face = "italic"), legend.position = "none")

ggsave("SDMad_RspOE_cyoglaIII_Kvalue.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")
```


#Figure 4E

```{r}
#SD5, III from cyo/gla
data <- data.frame(
  kValues = c(0.996666667,0.973404255,0.965909091,0.995049505,0.983108108,0.967741935,0.994413408,1,
              0.997844828,0.986988848,0.993814433,0.989690722,0.997252747,0.995859213,0.99382716,0.993150685,0.977272727),
  Genotype = c(rep("Iso1", 8), rep("RspOE", 9)))
data$Genotype <= factor(data$Genotype, levels = c("Iso1", "RspOE"))

ggplot(data, aes(x = Genotype, y = kValues, fill = Genotype)) +
  geom_boxplot(position = position_dodge(0.7), width = 0.65) +
  labs(x = NULL, y = expression("Prop. of " * italic("SD") * " Progeny")) +
  scale_fill_manual(values = c("dodgerblue3", "lightskyblue")) +
  ylim(c(0.5,1)) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20, face = "italic"), legend.position = "none")

ggsave("SD5_RspOE_cyoglaIII_Kvalue.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")
```

# Supplemental Figure 1A

```{r}
FC_Points_SDMad <- normCounts_SDMad_R16_Gla_smRNA[grepl("Rsp", rownames(normCounts_SDMad_R16_Gla_smRNA)) == TRUE,]
FC_Points_SDMad <- data.frame(Group = c(rep("R16/Gla(MAD)", 3), rep("SDMad/Gla", 3)),
                              Count = as.numeric(FC_Points_SDMad[1,]))

FC_Points_SD5 <- normCounts_SD5_R16_Gla_smRNA[grepl("Rsp", rownames(normCounts_SD5_R16_Gla_smRNA)) == TRUE,]
FC_Points_SD5 <- data.frame(Group = c(rep("R16/Gla(SD5)", 3), rep("SD5/Gla", 3)),
                              Count = as.numeric(FC_Points_SD5[1,]))


points <- bind_rows(
  FC_Points_SDMad,
  FC_Points_SD5
)

points$Pair <- rep(c("SDMad","SD5"),
                   times = c(nrow(FC_Points_SDMad),
                             nrow(FC_Points_SD5)))

points$Pair <- factor(points$Pair, levels=c("SDMad","SD5"))
points$Group <- factor(points$Group,
                       levels=c("R16/Gla(MAD)","SDMad/Gla",
                                "R16/Gla(SD5)","SD5/Gla"))

summary_df <- points |>
  dplyr::group_by(Pair, Group) |>
  dplyr::summarise(
    Mean = mean(Count),
    SD = sd(Count),
    .groups="drop"
  )

summary_df$Group <- factor(summary_df$Group,
                           levels = c("R16/Gla(MAD)","SDMad/Gla",
                                      "R16/Gla(SD5)","SD5/Gla"))

points$Group <- factor(points$Group,
                       levels = levels(summary_df$Group))

summary_Mad <- summary_df[grepl("Mad", summary_df$Pair) == TRUE, ]
summary_5 <- summary_df[grepl("SD5", summary_df$Pair) == TRUE, ]

points_Mad <- points[grepl("Mad", points$Pair) == TRUE, ]
points_5 <- points[grepl("SD5", points$Pair) == TRUE, ]

ggplot(summary_Mad, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_Mad,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("gray","seagreen")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("smRNA_CPMPlot_SDMad_Gla.pdf", width = 8, height = 6, units = c("in"), bg = "transparent")

ggplot(summary_5, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_5,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("gray","dodgerblue3")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("smRNA_CPMPlot_SD5_Gla.pdf", width = 8, height = 6, units = c("in"), bg = "transparent")
```

# Supplemental Figure 1B

```{r}
piRNALoci <- c("Rsp", "1pt688","piRNA_cluster_38C2", "piRNA_cluster_38C1", "piRNA_cluster_flamenco", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_42AB")
piRNALoci <- factor(piRNALoci, levels = c("Rsp", "1pt688","piRNA_cluster_38C1","piRNA_cluster_38C2", "piRNA_cluster_42AB", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_flamenco"))
gene_data <- data.frame(
  Gene = piRNALoci, 
  logFC_SDMad = SDMad_R16_smRNA_Gla$LogFC[match(piRNALoci, SDMad_R16_smRNA_Gla$Name)], logFC_SD5 = SD5_R16_smRNA_Gla$LogFC[match(piRNALoci, SD5_R16_smRNA_Gla$Name)], 
  p.Adj_SDMad = SDMad_R16_smRNA_Gla$p.Adj[match(piRNALoci, SDMad_R16_smRNA_Gla$Name)],  p.Adj_SD5 = SD5_R16_smRNA_Gla$p.Adj[match(piRNALoci, SD5_R16_smRNA_Gla$Name)])

df_long <- gene_data %>%
  pivot_longer(cols = starts_with("logFC"),
               names_to = "Condition",
               values_to = "logFC") %>%
  mutate(Condition = sub("logFC_", "", Condition)) %>%
  left_join(
    gene_data %>%
      pivot_longer(cols = starts_with("p.Adj"),
                   names_to = "Condition_p",
                   values_to = "p.Adj") %>%
      mutate(Condition = sub("p.Adj_", "", Condition_p)) %>%
      dplyr::select(Gene, Condition, p.Adj),
    by = c("Gene", "Condition")
  ) %>%
  mutate(sig = case_when(p.Adj <= 0.001 ~ "***",p.Adj <= 0.01  ~ "**",p.Adj <= 0.05  ~ "*",TRUE ~ ""))

ggplot(df_long, aes(x = Gene, y = Condition, fill = logFC)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sig), color = "black", size = 5) +
  scale_fill_gradient2(low = "dodgerblue3", mid = "white", high = "red2", midpoint = 0, name = "Log2FC") +
  scale_x_discrete(labels = c(
    "Rsp" = "Rsp",
    "1pt688" = "1.688",
    "piRNA_cluster_38C2" = "38C2",
    "piRNA_cluster_38C1" = "38C1",
    "piRNA_cluster_flamenco" = "Flamenco",
    "piRNA_cluster_80F" = "80F",
    "piRNA_cluster_20A" = "20A",
    "piRNA_cluster_42AB" = "42AB"
  )) +
  scale_y_discrete(labels = c(
    "SDMad" = "SDMad/Gla",
    "SDRev" = "SDRev/Gla",
    "SD5" = "SD5/Gla"
  )) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title = element_blank(), legend.text = element_text(size = 15), legend.title = element_text(size = 15))

ggsave("smRNA_HeatPlot_Gla.pdf", width = 10, height = 5, bg = "transparent")
```

# Supplemental Figure 5A

```{r}
piRNALoci <- c("Rsp", "1pt688","piRNA_cluster_38C2", "piRNA_cluster_38C1", "piRNA_cluster_flamenco", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_42AB")
piRNALoci <- factor(piRNALoci, levels = c("Rsp", "1pt688","piRNA_cluster_38C1","piRNA_cluster_38C2", "piRNA_cluster_42AB", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_flamenco"))
gene_data <- data.frame(
  Gene = piRNALoci, 
  logFC_SDMad = SDMad_R16_totRNA_Repeats_Gla$LogFC[match(piRNALoci, SDMad_R16_totRNA_Repeats_Gla$Name)], logFC_SD5 = SD5_R16_totRNA_Repeats_Gla$LogFC[match(piRNALoci, SD5_R16_totRNA_Repeats_Gla$Name)], 
  p.Adj_SDMad = SDMad_R16_totRNA_Repeats_Gla$p.Adj[match(piRNALoci, SDMad_R16_totRNA_Repeats_Gla$Name)], p.Adj_SD5 = SD5_R16_totRNA_Repeats_Gla$p.Adj[match(piRNALoci, SD5_R16_totRNA_Repeats_Gla$Name)])

df_long <- gene_data %>%
  pivot_longer(cols = starts_with("logFC"),
               names_to = "Condition",
               values_to = "logFC") %>%
  mutate(Condition = sub("logFC_", "", Condition)) %>%
  left_join(
    gene_data %>%
      pivot_longer(cols = starts_with("p.Adj"),
                   names_to = "Condition_p",
                   values_to = "p.Adj") %>%
      mutate(Condition = sub("p.Adj_", "", Condition_p)) %>%
      dplyr::select(Gene, Condition, p.Adj),
    by = c("Gene", "Condition")
  ) %>%
  mutate(sig = case_when(p.Adj <= 0.001 ~ "***",p.Adj <= 0.01  ~ "**",p.Adj <= 0.05  ~ "*",TRUE ~ ""))

ggplot(df_long, aes(x = Gene, y = Condition, fill = logFC)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sig), color = "black", size = 5) +
  scale_fill_gradient2(low = "dodgerblue3", mid = "white", high = "red2", midpoint = 0, name = "Log2FC") +
  scale_x_discrete(labels = c(
    "Rsp" = "Rsp",
    "1pt688" = "1.688",
    "piRNA_cluster_38C2" = "38C2",
    "piRNA_cluster_38C1" = "38C1",
    "piRNA_cluster_flamenco" = "Flamenco",
    "piRNA_cluster_80F" = "80F",
    "piRNA_cluster_20A" = "20A",
    "piRNA_cluster_42AB" = "42AB"
  )) +
  scale_y_discrete(labels = c(
    "SDMad" = "SDMad/Gla",
    "SD5" = "SD5/Gla"
  )) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title = element_blank(), legend.text = element_text(size = 15), legend.title = element_text(size = 15))

ggsave("totRNA_HeatPlot_Gla.pdf", width = 10, height = 3, bg = "transparent")
```

# Supplemental Figure 5B

```{r}
piRNALoci <- c("Rsp", "1pt688","piRNA_cluster_38C2", "piRNA_cluster_38C1", "piRNA_cluster_flamenco", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_42AB")
piRNALoci <- factor(piRNALoci, levels = c("Rsp", "1pt688","piRNA_cluster_38C1","piRNA_cluster_38C2", "piRNA_cluster_42AB", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_flamenco"))
gene_data <- data.frame(
  Gene = piRNALoci, 
  logFC_SDMad = SDMad_R16_totRNA_Repeats_Iso1$LogFC[match(piRNALoci, SDMad_R16_totRNA_Repeats_Iso1$Name)], logFC_SD5 = SD5_R16_totRNA_Repeats_Iso1$LogFC[match(piRNALoci, SD5_R16_totRNA_Repeats_Iso1$Name)], 
  p.Adj_SDMad = SDMad_R16_totRNA_Repeats_Iso1$p.Adj[match(piRNALoci, SDMad_R16_totRNA_Repeats_Iso1$Name)], p.Adj_SD5 = SD5_R16_totRNA_Repeats_Iso1$p.Adj[match(piRNALoci, SD5_R16_totRNA_Repeats_Iso1$Name)])

df_long <- gene_data %>%
  pivot_longer(cols = starts_with("logFC"),
               names_to = "Condition",
               values_to = "logFC") %>%
  mutate(Condition = sub("logFC_", "", Condition)) %>%
  left_join(
    gene_data %>%
      pivot_longer(cols = starts_with("p.Adj"),
                   names_to = "Condition_p",
                   values_to = "p.Adj") %>%
      mutate(Condition = sub("p.Adj_", "", Condition_p)) %>%
      dplyr::select(Gene, Condition, p.Adj),
    by = c("Gene", "Condition")
  ) %>%
  mutate(sig = case_when(p.Adj <= 0.001 ~ "***",p.Adj <= 0.01  ~ "**",p.Adj <= 0.05  ~ "*",TRUE ~ ""))

ggplot(df_long, aes(x = Gene, y = Condition, fill = logFC)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sig), color = "black", size = 5) +
  scale_fill_gradient2(low = "dodgerblue3", mid = "white", high = "red2", midpoint = 0, name = "Log2FC") +
  scale_x_discrete(labels = c(
    "Rsp" = "Rsp",
    "1pt688" = "1.688",
    "piRNA_cluster_38C2" = "38C2",
    "piRNA_cluster_38C1" = "38C1",
    "piRNA_cluster_flamenco" = "Flamenco",
    "piRNA_cluster_80F" = "80F",
    "piRNA_cluster_20A" = "20A",
    "piRNA_cluster_42AB" = "42AB"
  )) +
  scale_y_discrete(labels = c(
    "SDMad" = "SDMad/Iso1",
    "SD5" = "SD5/Iso1"
  )) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title = element_blank(), legend.text = element_text(size = 15), legend.title = element_text(size = 15))

ggsave("totRNA_HeatPlot_Iso1.pdf", width = 10, height = 3, bg = "transparent")
```

# Supplemental Figure 5C

```{r}
SDMad_R16_DEList <- SDMad_R16_totRNA_Iso1[SDMad_R16_totRNA_Iso1$p.Adj <= 0.05,]
SDMad_R16_DEList_Names <- SDMad_R16_DEList$Name

SD5_R16_DEList <- SD5_R16_totRNA_Iso1[SD5_R16_totRNA_Iso1$p.Adj <= 0.05,]
SD5_R16_DEList_Names <- SD5_R16_DEList$Name

individualization_GeneSet <- read.table("Individualization_GeneSet.txt")
colnames(individualization_GeneSet) <- c("SYMBOL", "FLYBASE")

SDMad_data <- SDMad_R16_totRNA_Iso1[SDMad_R16_totRNA_Iso1$Name %in% individualization_GeneSet$FLYBASE,]
SD5_data <- SD5_R16_totRNA_Iso1[SD5_R16_totRNA_Iso1$Name %in% individualization_GeneSet$FLYBASE,]
merged_Data_Iso1 <- merge(SDMad_data, SD5_data, by = "Name")

indData <- na.omit(data.frame(Gene = merged_Data_Iso1$SYMBOL.x, logFC_SDMad = merged_Data_Iso1$LogFC.x, p.Adj_SDMad = merged_Data_Iso1$p.Adj.x, logFC_SD5 = merged_Data_Iso1$LogFC.y, p.Adj_SD5 = merged_Data_Iso1$p.Adj.y))

write_tsv(indData, "supplementalTables/individualizationTable_Iso1.tsv")

df_long_indData <- indData %>%
  pivot_longer(cols = starts_with("logFC"),
               names_to = "Condition",
               values_to = "logFC") %>%
  mutate(Condition = sub("logFC_", "", Condition)) %>%
  left_join(
    indData %>%
      pivot_longer(cols = starts_with("p.Adj"),
                   names_to = "Condition_p",
                   values_to = "p.Adj") %>%
      mutate(Condition = sub("p.Adj_", "", Condition_p)) %>%
      dplyr::select(Gene, Condition, p.Adj),
    by = c("Gene", "Condition")
  ) %>%
  mutate(sig = case_when(p.Adj <= 0.001 ~ "***",p.Adj <= 0.01  ~ "**",p.Adj <= 0.05  ~ "*",TRUE ~ ""))

ggplot(df_long_indData, aes(x = Gene, y = Condition, fill = logFC)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "dodgerblue3", mid = "white", high = "red2", midpoint = 0, name = "log2FC") +
  theme_minimal() +
  geom_text(aes(label = sig, angle = 90), color = "black", size = 10, vjust = 0.75) +
  scale_y_discrete(labels = c("SDMad" = "SDMad/Iso1", "SD5" = "SD5/Iso1")) +
  theme(axis.text.x = element_text(size = 20, angle = 45, hjust = 1), axis.text.y = element_text(size = 30, face = "italic"), axis.title = element_blank(), legend.text = element_text(size = 40), legend.title = element_text(size = 40), legend.key.size = unit(0.5, "in")) 

ggsave("individualization_HeatPlot_Iso1_Supplement.pdf", width = 25, height = 6, bg = "transparent")
```

# Supplemental Figure 6

```{r}
SDMad_R16_Gla_TEs <- SDMad_R16_totRNA_Repeats_Gla[grepl("^FBgn", SDMad_R16_totRNA_Repeats_Gla$Name) == FALSE & grepl("SAT|Rsp|1pt688|luster|sland|rDNA|AT-ChX|Low_complexity|Simple_repeat|Satellite",SDMad_R16_totRNA_Repeats_Gla$Name) == FALSE,]
SDMad_R16_Gla_TEs <- SDMad_R16_Gla_TEs[c(1,3,5)]
SDMad_R16_Gla_TEs$Genotype <- rep("SDMad", length(SDMad_R16_Gla_TEs$Name))

SDMad_R16_Iso1_TEs <- SDMad_R16_totRNA_Repeats_Iso1[grepl("^FBgn", SDMad_R16_totRNA_Repeats_Iso1$Name) == FALSE & grepl("SAT|Rsp|1pt688|sland|rDNA|AT-ChX|Low_complexity|Simple_repeat|Satellite",SDMad_R16_totRNA_Repeats_Iso1$Name) == FALSE,]
SDMad_R16_Iso1_TEs <- SDMad_R16_Iso1_TEs[c(1,3,5)]

SD5_R16_Gla_TEs <- SD5_R16_totRNA_Repeats_Gla[grepl("^FBgn", SD5_R16_totRNA_Repeats_Gla$Name) == FALSE & grepl("SAT|Rsp|1pt688|luster|sland|rDNA|AT-ChX|Low_complexity|Simple_repeat|Satellite",SD5_R16_totRNA_Repeats_Gla$Name) == FALSE,]
SD5_R16_Gla_TEs <- SD5_R16_Gla_TEs[c(1,3,5)]
SD5_R16_Gla_TEs$Genotype <- rep("SD5", length(SD5_R16_Gla_TEs$Name))

plotData <- rbind(SDMad_R16_Gla_TEs, SD5_R16_Gla_TEs)

TE_Fams <- read.table("TE_Families.tsv")
TE_Fams <- data.frame(Name = TE_Fams$V1, Family = TE_Fams$V2)

plotData <- plotData %>%
  mutate(
    sig = case_when(
      p.Adj <= 0.0001 ~ "***",
      p.Adj <= 0.001  ~ "**",
      p.Adj <= 0.01   ~ "*",
      TRUE ~ ""))

ggplot(plotData, aes(x = Name, y = Genotype, fill = LogFC)) +
  geom_tile(color = "grey80") +
  geom_text(aes(label = sig), size = 5) +
  scale_fill_gradient2(
    low = "dodgerblue3",
    mid = "white",
    high = "red2",
    midpoint = 0,
    limits=c(-1,1),
    oob=scales::squish,
    name = "Log2FC"
  ) +
  scale_y_discrete(labels = c(
    "SDMad" = "SDMad/Gla",
    "SD5" = "SD5/Gla")) +
  theme_minimal(base_size = 16) +
  theme(axis.text.y = element_text(size = 20),axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1, size = 16, face = "italic"))

ggsave("TEs_HeatPlot_Gla.pdf", width = 10, height = 4, bg = "transparent")

```

# Supplemental Figure 7A

```{r}
SDMadvR16_Gla_DotPlotData <- read_csv("PANGEA_Results/SDMadvR16_Gla_PANGEA.csv")
WGCNA_PangeaDotPlot(SDMadvR16_Gla_DotPlotData, dotplotprefix = "SDMadvR16_Gla", numSets = 15)
```

# Supplemental Figure 7B

```{r}
SD5vR16_Gla_DotPlotData <- read_csv("PANGEA_Results/SD5vR16_Gla_PANGEA.csv")
WGCNA_PangeaDotPlot(SD5vR16_Gla_DotPlotData, dotplotprefix = "SD5vR16_Gla", numSets = 15)
```

# Supplemental Figure 8

```{r}
top20_Symbols <- top20$SYMBOL

gene_data <- data.frame(
  Gene = top20_Symbols, 
  logFC_DGE = SDMad_SDRev_DGE_Iso1$LogFC[match(top20_Symbols, SDMad_SDRev_DGE_Iso1$SYMBOL)], logFC_totRNA = SDMad_SDRev_totRNA_Iso1$LogFC[match(top20_Symbols, SDMad_SDRev_totRNA_Iso1$SYMBOL)], 
  p.Adj_DGE = SDMad_SDRev_DGE_Iso1$p.Adj[match(top20_Symbols, SDMad_SDRev_DGE_Iso1$SYMBOL)], p.Adj_totRNA = SDMad_SDRev_totRNA_Iso1$p.Adj[match(top20_Symbols, SDMad_SDRev_totRNA_Iso1$SYMBOL)])

df_long <- gene_data %>%
  pivot_longer(cols = starts_with("logFC"),
               names_to = "Condition",
               values_to = "logFC") %>%
  mutate(Condition = sub("logFC_", "", Condition)) %>%
  left_join(
    gene_data %>%
      pivot_longer(cols = starts_with("p.Adj"),
                   names_to = "Condition_p",
                   values_to = "p.Adj") %>%
      mutate(Condition = sub("p.Adj_", "", Condition_p)) %>%
      dplyr::select(Gene, Condition, p.Adj),
    by = c("Gene", "Condition")
  ) %>%
  mutate(sig = case_when(p.Adj <= 0.001 ~ "***",p.Adj <= 0.01  ~ "**",p.Adj <= 0.05  ~ "*",TRUE ~ ""))

ggplot(df_long, aes(x = Condition, y = Gene, fill = logFC)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sig), color = "black", size = 5) +
  scale_fill_gradient2(low = "dodgerblue3", mid = "white", high = "red2", midpoint = 0, limits = c(-5, 5), oob = scales::squish, name = "Log2FC") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title = element_blank(), legend.text = element_text(size = 15), legend.title = element_text(size = 15))

ggsave("DGE_totRNA_HeatPlot.pdf", width = 6, height = 5, bg = "transparent")
```

# Supplemental Figure 10B

```{r}
# piRNA Gene Relative Expression
R16_Counts1 <- read.table("totRNA_Counts/R16-Gla-1.simplified.counts_fam")
R16_Counts1 <- data.frame(Name = R16_Counts1$V1, NumReads = R16_Counts1$V2)

R16_Counts2 <- read.table("totRNA_Counts/R16-Gla-2.simplified.counts_fam")
R16_Counts2 <- data.frame(Name = R16_Counts2$V1, NumReads = R16_Counts2$V2)

R16_Counts3 <- read.table("totRNA_Counts/R16-Gla-3.simplified.counts_fam")
R16_Counts3 <- data.frame(Name = R16_Counts3$V1, NumReads = R16_Counts3$V2)

Rhino <- c(TPM_calc(c("FBgn0004400"), R16_Counts1)$TPM, TPM_calc(c("FBgn0004400"), R16_Counts2)$TPM, TPM_calc(c("FBgn0004400"), R16_Counts3)$TPM)

Kipferl <- c(TPM_calc(c("FBgn0014931"), R16_Counts1)$TPM, TPM_calc(c("FBgn0014931"), R16_Counts2)$TPM, TPM_calc(c("FBgn0014931"), R16_Counts3)$TPM)

Cutoff <- c(TPM_calc(c("FBgn0260932"), R16_Counts1)$TPM, TPM_calc(c("FBgn0260932"), R16_Counts2)$TPM, TPM_calc(c("FBgn0260932"), R16_Counts3)$TPM)

Bootlegger <- c(TPM_calc(c("FBgn0033374"), R16_Counts1)$TPM, TPM_calc(c("FBgn0033374"), R16_Counts2)$TPM, TPM_calc(c("FBgn0033374"), R16_Counts3)$TPM)

data <- data.frame(Group = c("Rhino", "Kipferl", "Cutoff", "Bootlegger"), TPM = c(mean(Rhino), mean(Kipferl), mean(Cutoff), mean(Bootlegger)), StDev = c(sd(Rhino), sd(Kipferl), sd(Cutoff), sd(Bootlegger)))

ggplot(data, aes(y = TPM, fill = Group)) +
  geom_bar(aes(x = Group, y = TPM), stat = "identity", width = 0.6) +
  scale_fill_manual(values=c("chocolate4", "royalblue3", "darkgreen", "goldenrod")) +
  labs(x = NULL, y = "Fold Change ± StDv") +
  theme_classic() +
  geom_errorbar(aes(x = Group, ymin = data$TPM - data$StDev, ymax = data$TPM + data$StDev), width = 0.1) +
  theme(legend.position = "none", axis.text.x = element_text(size = 20, face = "italic"), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20), legend.text = element_text(size = 15))

ggsave("piRNAGene_TPM.pdf", width = 8, height = 4, bg = "transparent")
```

# Supplemental Figure 10D

```{r}
# Kip RT Barplot
data <- data.frame(Genotype = c("Ral309_Ovary", "KipKO_Ovary", "Ral309_Testis","KipKO_Testis"), IntDen = c(1.034, 0.027, 0.193, 0.0046))
  
  data$Genotype <- factor(data$Genotype, levels = data$Genotype)
  
  ggplot(data, aes(y = IntDen, fill = Genotype)) +
    geom_bar(aes(x = Genotype, y = IntDen), stat = "identity", width = 0.6) +
    scale_fill_manual(values=c("black", "black", "gray", "grey")) +
    labs(x = NULL, y = "Ratio of IntDen (kip/rp49)") +
    theme_classic() +
    scale_x_discrete(labels = c(
    "Ral309_Ovary" = "Ral309 Ovary",
    "KipKO_Ovary" = "KipKO Ovary",
    "Ral309_Testis" = "Ral309 Testis",
    "KipKO_Testis" = "KipKO Testis"
  )) +
    theme(legend.position = "none", axis.text.x = element_text(size = 20, angle = 45, hjust = 1), axis.text.y = element_text(size = 16), axis.title.y = element_text(size = 24)) 
    
  
ggsave("KipRT_Quant.pdf", width = 4, height = 6, bg = "transparent")
```

# Supplemental Figure 10E

```{r}
kipferl <- read.table("smRNA_counts/Baumgartner_2024/KipferlMutant.out_fam")
RhinoG31D <- read.table("smRNA_counts/Baumgartner_2024/RhinoG31D.out_fam")
RhinoMut <- read.table("smRNA_counts/Baumgartner_2024/RhinoMutant.out_fam")
w1118 <- read.table("smRNA_counts/Baumgartner_2024/W1118.out_fam")

element <- "1pt688"
kip_CPM <- extractCPM(kipferl, element)
RhinoG31D_CPM <- extractCPM(RhinoG31D, element)
w1118_CPM <- extractCPM(w1118, element)

data <- data.frame(Group = c("Kipferl", "Rhino G31D", "W1118"), CPM = c(kip_CPM, RhinoG31D_CPM, w1118_CPM))

ggplot(data, aes(y = CPM, fill = Group)) +
  geom_bar(aes(x = Group, y = CPM), stat = "identity", width = 0.6) +
  scale_fill_manual(values=c("navy", "limegreen", "darkred")) +
  labs(x = NULL, y = "TPM") +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 15, face = "italic"), axis.text.y = element_text(size = 12), axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20), legend.text = element_text(size = 15))

ggsave("Baumgartner_1pt688.pdf", width = 4, height = 4, bg = "transparent")
```

# Supplemental Figure 10F

```{r}
kipferl <- read.table("smRNA_counts/Baumgartner_2024/KipferlMutant.out_fam")
RhinoG31D <- read.table("smRNA_counts/Baumgartner_2024/RhinoG31D.out_fam")
RhinoMut <- read.table("smRNA_counts/Baumgartner_2024/RhinoMutant.out_fam")
w1118 <- read.table("smRNA_counts/Baumgartner_2024/W1118.out_fam")

element <- "Rsp"
kip_CPM <- extractCPM(kipferl, element)
RhinoG31D_CPM <- extractCPM(RhinoG31D, element)
w1118_CPM <- extractCPM(w1118, element)

data <- data.frame(Group = c("Kipferl", "Rhino G31D", "W1118"), CPM = c(kip_CPM, RhinoG31D_CPM, w1118_CPM))

ggplot(data, aes(y = CPM, fill = Group)) +
  geom_bar(aes(x = Group, y = CPM), stat = "identity", width = 0.6) +
  scale_fill_manual(values=c("navy", "limegreen", "darkred")) +
  labs(x = NULL, y = "CPM") +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 15, face = "italic"), axis.text.y = element_text(size = 12), axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20), legend.text = element_text(size = 15))

ggsave("Baumgartner_Rsp.pdf", width = 4, height = 4, bg = "transparent")
```

# Supplemental Figure 11A

```{r}
piRNALoci <- c("Rsp", "1pt688","piRNA_cluster_38C2", "piRNA_cluster_38C1", "piRNA_cluster_flamenco", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_42AB")
piRNALoci <- factor(piRNALoci, levels = c("Rsp", "1pt688","piRNA_cluster_38C1","piRNA_cluster_38C2", "piRNA_cluster_42AB", "piRNA_cluster_80F", "piRNA_cluster_20A", "piRNA_cluster_flamenco"))
gene_data <- data.frame(
  Gene = piRNALoci, 
  #logFC_SDMad = SDMad_RspOE_SDMad_smRNA_Iso1$LogFC[match(piRNALoci, SDMad_RspOE_SDMad_smRNA_Iso1$Name)], 
  #logFC_SD5 = SD5_RspOE_SD5_smRNA_Iso1$LogFC[match(piRNALoci, SD5_RspOE_SD5_smRNA_Iso1$Name)], 
  logFC_SDMad_dsRed = SDMad_RspOE_dsRed_SDMad_smRNA_Iso1$LogFC[match(piRNALoci, SDMad_RspOE_dsRed_SDMad_smRNA_Iso1$Name)],
  logFC_SD5_dsRed = SD5_RspOE_dsRed_SD5_smRNA_Iso1$LogFC[match(piRNALoci, SD5_RspOE_dsRed_SD5_smRNA_Iso1$Name)],
  #p.Adj_SDMad = SDMad_RspOE_SDMad_smRNA_Iso1$p.Adj[match(piRNALoci, SDMad_RspOE_SDMad_smRNA_Iso1$Name)], 
  #p.Adj_SD5 = SD5_RspOE_SD5_smRNA_Iso1$p.Adj[match(piRNALoci, SD5_RspOE_SD5_smRNA_Iso1$Name)])
  p.Adj_SDMad_dsRed = SDMad_RspOE_dsRed_SDMad_smRNA_Iso1$p.Adj[match(piRNALoci, SDMad_RspOE_dsRed_SDMad_smRNA_Iso1$Name)], 
  p.Adj_SD5_dsRed = SD5_RspOE_dsRed_SD5_smRNA_Iso1$p.Adj[match(piRNALoci, SD5_RspOE_dsRed_SD5_smRNA_Iso1$Name)])


df_long <- gene_data %>%
  pivot_longer(cols = starts_with("logFC"),
               names_to = "Condition",
               values_to = "logFC") %>%
  mutate(Condition = sub("logFC_", "", Condition)) %>%
  left_join(
    gene_data %>%
      pivot_longer(cols = starts_with("p.Adj"),
                   names_to = "Condition_p",
                   values_to = "p.Adj") %>%
      mutate(Condition = sub("p.Adj_", "", Condition_p)) %>%
      dplyr::select(Gene, Condition, p.Adj),
    by = c("Gene", "Condition")
  ) %>%
  mutate(sig = case_when(p.Adj <= 0.001 ~ "***",p.Adj <= 0.01  ~ "**",p.Adj <= 0.05  ~ "*",TRUE ~ ""))

ggplot(df_long, aes(x = Gene, y = Condition, fill = logFC)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sig), color = "black", size = 8) +
  scale_fill_gradient2(low = "dodgerblue3", mid = "white", high = "red2", midpoint = 0, name = "log2FC") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 20, vjust = 1, face = "italic"), axis.text.y = element_text(size = 15), axis.title = element_blank(), legend.text = element_text(size = 15), legend.title = element_text(size = 20)) +
  scale_x_discrete(labels = c(
    "Rsp" = "Rsp",
    "1pt688" = "1.688",
    "piRNA_cluster_38C2" = "38C2",
    "piRNA_cluster_38C1" = "38C1",
    "piRNA_cluster_flamenco" = "Flamenco",
    "piRNA_cluster_80F" = "80F",
    "piRNA_cluster_20A" = "20A",
    "piRNA_cluster_42AB" = "42AB"
  ))  

ggsave("smRNA_HeatPlot_RspOE-dsRed.pdf", width = 10, height = 5, bg = "transparent")
```

# Supplemental Figure 11B

```{r}
SDMad_1 <- read.table("smRNA_counts/all_summedbyFam/SDMad_Iso1_new_1_R1.out_fam")
SDMad_2 <- read.table("smRNA_counts/all_summedbyFam/SDMad_Iso1_new_2_R1.out_fam")
SDMad_3 <- read.table("smRNA_counts/all_summedbyFam/SDMad_Iso1_new_3_R1.out_fam")
SDMadRspOE_1 <- read.table("smRNA_counts/all_summedbyFam/SDMad_RspOE_ori_new_1_R1.out_fam")
SDMadRspOE_2 <- read.table("smRNA_counts/all_summedbyFam/SDMad_RspOE_ori_new_2_R1.out_fam")
SDMadRspOE_3 <- read.table("smRNA_counts/all_summedbyFam/SDMad_RspOE_ori_new_3_R1.out_fam")
SD5_1 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_new_1_R1.out_fam")
SD5_2 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_new_2_R1.out_fam")
SD5_3 <- read.table("smRNA_counts/all_summedbyFam/SD5_Iso1_new_3_R1.out_fam")
SD5RspOE_1 <- read.table("smRNA_counts/all_summedbyFam/SD5_RspOE_ori_new_1_R1.out_fam")
SD5RspOE_2 <- read.table("smRNA_counts/all_summedbyFam/SD5_RspOE_ori_new_2_R1.out_fam")
SD5RspOE_3 <- read.table("smRNA_counts/all_summedbyFam/SD5_RspOE_ori_new_3_R1.out_fam")

element <- "Rsp"
SDMad_CPM <- mean(extractCPM(SDMad_1, element), extractCPM(SDMad_2, element), extractCPM(SDMad_3, element))
SDMad_StD <- sd(c(extractCPM(SDMad_1, element), extractCPM(SDMad_2, element), extractCPM(SDMad_3, element)))
SDMadRspOE_CPM <- mean(extractCPM(SDMadRspOE_1, element), extractCPM(SDMadRspOE_2, element), extractCPM(SDMadRspOE_3, element))
SDMadRspOE_StD <- sd(c(extractCPM(SDMadRspOE_1, element), extractCPM(SDMadRspOE_2, element), extractCPM(SDMadRspOE_3, element)))
SD5_CPM <- mean(extractCPM(SD5_1, element), extractCPM(SD5_2, element), extractCPM(SD5_3, element))
SD5_StD <- sd(c(extractCPM(SD5_1, element), extractCPM(SD5_2, element), extractCPM(SD5_3, element)))
SD5RspOE_CPM <- mean(extractCPM(SD5RspOE_1, element), extractCPM(SD5RspOE_2, element), extractCPM(SD5RspOE_3, element))
SD5RspOE_StD <- sd(c(extractCPM(SD5RspOE_1, element), extractCPM(SD5RspOE_2, element), extractCPM(SD5RspOE_3, element)))

# RspOE Expression Plot
df_wide <- data.frame(
  Condition = c("SDMad/Iso1 vs SDMad/RspOE", "SD5/Iso1 vs SD5/RspOE"),
  Control = c(SDMad_CPM, SD5_CPM),
  Treatment = c(SDMadRspOE_CPM, SD5RspOE_CPM),
  StDevC = c(SDMad_StD, SD5_StD),
  StDevT = c(SDMadRspOE_StD, SD5RspOE_StD)
)

df_wide$Condition <- factor(df_wide$Condition, levels = c("SDMad/Iso1 vs SDMad/RspOE", "SD5/Iso1 vs SD5/RspOE"))

df_long <- df_wide %>%
  dplyr::select(Condition, Control, Treatment, StDevC, StDevT) %>%
  pivot_longer(
    cols = c(Control, Treatment),
    names_to = "Group",
    values_to = "Value"
  ) %>%
  mutate(StDev = ifelse(Group == "Control", StDevC, StDevT)) %>%
  dplyr::select(Condition, Group, Value, StDev)

df_long$BarColor <- c("seagreen", "seagreen3", "dodgerblue3", "cornflowerblue")
df_long$BarColor <- factor(df_long$BarColor, levels = c("seagreen", "seagreen3", "dodgerblue3", "cornflowerblue"))

ggplot(df_long, aes(x = Condition, y = Value, fill = BarColor)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8),
           width = 0.8, color = "black") +
  geom_errorbar(
    aes(ymin = Value - StDev, ymax = Value + StDev, group = BarColor),
    position = position_dodge(width = 0.8),
    width = 0.2
  ) +
  scale_fill_identity() +  # uses exact colors in BarColor
  labs(x = "", y = expression(italic("Rsp") * " CPM")) +
  theme_minimal() +
  theme(axis.title.y = element_text(size = 30),
        axis.text.y = element_text(size = 26),
        legend.position = "none", panel.grid = element_blank())

ggsave("rspOE-dsRed_smRNACounts_DESeq2.pdf", width = 10, height = 6, bg = "transparent")
```

# New Supplement with fixed Rsp Counts

```{r}
dsRed_Points_SDMad <- normCounts_SDMad_RspOE_dsRed_SDMad_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SDMad_RspOE_dsRed_SDMad_Iso1_smRNA)) == TRUE,]
dsRed_Points_SDMad <- data.frame(Group = c(rep("SDMad/Iso1", 3), rep("SDMad/RspOE", 3)),
                              Count = as.numeric(dsRed_Points_SDMad[1,]))

dsRed_Points_SD5 <- normCounts_SD5_RspOE_dsRed_SD5_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SD5_RspOE_dsRed_SD5_Iso1_smRNA)) == TRUE,]
dsRed_Points_SD5 <- data.frame(Group = c(rep("SD5/Iso1", 3), rep("SD5/RspOE", 3)),
                              Count = as.numeric(dsRed_Points_SD5[1,]))


points <- bind_rows(
  dsRed_Points_SDMad,
  dsRed_Points_SD5
)

points$Pair <- rep(c("SDMad","SD5"),
                   times = c(nrow(dsRed_Points_SDMad),
                             nrow(dsRed_Points_SD5)))

points$Pair <- factor(points$Pair, levels=c("SDMad","SD5"))
points$Group <- factor(points$Group,
                       levels=c("SDMad/Iso1","SDMad/RspOE",
                                "SD5/Iso1","SD5/RspOE"))

summary_df <- points |>
  dplyr::group_by(Pair, Group) |>
  dplyr::summarise(
    Mean = mean(Count),
    SD = sd(Count),
    .groups="drop"
  )

summary_df$Group <- factor(summary_df$Group,
                           levels = c("SDMad/Iso1","SDMad/RspOE",
                                      "SD5/Iso1","SD5/RspOE"))

points$Group <- factor(points$Group,
                       levels = levels(summary_df$Group))

summary_Mad <- summary_df[grepl("Mad", summary_df$Pair) == TRUE, ]
summary_5 <- summary_df[grepl("SD5", summary_df$Pair) == TRUE, ]

points_Mad <- points[grepl("Mad", points$Pair) == TRUE, ]
points_5 <- points[grepl("SD5", points$Pair) == TRUE, ]

ggplot(summary_Mad, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_Mad,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("seagreen","seagreen3")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("rspOE_dsRed_smRNACounts_SDMad_DESeq2.pdf", width = 6, height = 6, bg = "transparent")

ggplot(summary_5, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_5,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("dodgerblue3","cornflowerblue")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("rspOE_dsRed_smRNACounts_SD5_DESeq2.pdf", width = 6, height = 6, bg = "transparent")
```

# Supplemental Figure 11C

```{r}
data <- data.frame(
  kValues = c(0.820809249,0.845070423,0.75,0.903225806,0.726190476,0.834920635,0.909465021,0.888586957,
              0.817857143,0.929292929,0.887530562,0.854368932,0.852130326,0.817910448,0.795977011,0.897058824,0.888888889,0.920289855),
  Genotype = c(rep("Iso1", 8), rep("RspOE-dsRed", 10)))

data$Genotype <= factor(data$Genotype, levels = c("Iso1", "RspOE-dsRed"))

ggplot(data, aes(x = Genotype, y = kValues, fill = Genotype)) +
  geom_boxplot(position = position_dodge(0.7), width = 0.65) +
  labs(x = NULL, y = expression("Prop. of " * italic("SD") * " Progeny")) +
  scale_fill_manual(values = c("seagreen", "springgreen2")) +
  ylim(c(0.5,1)) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20, face = "italic"), legend.position = "none")

ggsave("SDMad_RspOEdsRed_cyoglaIII_Kvalue.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")
```

# Supplemental Figure 11D

```{r}
data <- data.frame(
  kValues = c(0.996666667,0.973404255,0.965909091,0.995049505,0.983108108,0.967741935,0.994413408,1,
              0.986111111,0.99410609,0.991758242,1,0.990888383,0.987531172,0.978571429,0.993630573),
  Genotype = c(rep("Iso1", 8), rep("RspOE-dsRed", 8)))
data$Genotype <= factor(data$Genotype, levels = c("Iso1", "RspOE-dsRed"))

ggplot(data, aes(x = Genotype, y = kValues, fill = Genotype)) +
  geom_boxplot(position = position_dodge(0.7), width = 0.65) +
  labs(x = NULL, y = expression("Prop. of " * italic("SD") * " Progeny")) +
  scale_fill_manual(values = c("dodgerblue3", "lightskyblue")) +
  ylim(c(0.5,1)) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20, face = "italic"), legend.position = "none")

ggsave("SD5_RspOEdsRED_cyoglaIII_Kvalue.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")
```

# Kip KD Panel A

```{r}
# KipKD K values: Iso1
data <- data.frame(
  White = c(0.992, 0.987, 0.995, 0.985, 0.981, 0.942, 0.989, 1, 0.983),
  Kip = c(0.847, 0.928, 0.837, 0.858, 0.896, 0.943, 0.919, NA, NA)
)

long_data <- pivot_longer(data, cols = everything(), names_to = "shRNA", values_to = "K_Val")

long_data$shRNA <- factor(long_data$shRNA, levels = c("White", "Kip"))

ggplot(long_data, aes(x = shRNA, y = K_Val, fill = shRNA)) +
  geom_boxplot(outlier.shape = 21, outlier.fill = "white", outlier.color = "black") +
  scale_x_discrete(labels = c("White" = "White shRNA",
                              "Kip" = "Kipferl shRNA")) +
  scale_fill_manual(values = c("darkgrey", "seagreen")) +
  scale_y_continuous(limits = c(0.5,1)) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title.x = element_blank())

ggsave("Iso1_Bam_Kvalue.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")
```

# Kip KD Panel B

```{r}
# KipKD K values: C8
data <- data.frame(
  White = c(0.848,0.827,0.894,0.830,0.789,0.756,0.718,0.959,0.932,0.910),
  Kip = c(0.784,0.596,0.569,0.729,0.840,0.713,0.808,0.723,0.706,NA)
)

long_data <- pivot_longer(data, cols = everything(), names_to = "shRNA", values_to = "K_Val")

long_data$shRNA <- factor(long_data$shRNA, levels = c("White", "Kip"))

ggplot(long_data, aes(x = shRNA, y = K_Val, fill = shRNA)) +
  geom_boxplot(outlier.shape = 21, outlier.fill = "white", outlier.color = "black") +
  scale_x_discrete(labels = c("White" = "White shRNA",
                              "Kip" = "Kipferl shRNA")) +
  scale_fill_manual(values = c("darkgrey", "seagreen")) +
  scale_y_continuous(limits = c(0.5,1)) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15), axis.title.x = element_blank())

ggsave("C8_Bam_Kvalue.pdf", width = 4, height = 4, units = c("in"), bg = "transparent")
```

```{r}
FC_Points_FBgn0036294 <- normCounts_SDMad_SDRev_Iso1_DGE[grepl("FBgn0038196", rownames(normCounts_SDMad_SDRev_Iso1_DGE)) == TRUE,]
FC_Points_FBgn0036294 <- data.frame(Group = c(rep("SDMadRev/Iso1", 3), rep("SDMad/Iso1", 3)),
                              Count = as.numeric(FC_Points_FBgn0036294[1,]))

FC_Points_SDRev <- normCounts_SDMadRev_R16_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SDMadRev_R16_Iso1_smRNA)) == TRUE,]
FC_Points_SDRev <- data.frame(Group = c(rep("SDRev/Iso1", 6), rep("R16/Iso1(REV)", 5)),
                              Count = as.numeric(FC_Points_SDRev[1,]))

FC_Points_SD5 <- normCounts_SD5_R16_Iso1_smRNA[grepl("Rsp", rownames(normCounts_SD5_R16_Iso1_smRNA)) == TRUE,]
FC_Points_SD5 <- data.frame(Group = c(rep("R16/Iso1(SD5)", 3), rep("SD5/Iso1", 3)),
                              Count = as.numeric(FC_Points_SD5[1,]))

FC_Points_SDRev <- normCounts_SDMad_SDRev_Iso1_DGE[grepl("Rsp", rownames(normCounts_SDMad_SDRev_Iso1_DGE)) == TRUE,]
FC_Points_SDRev <- data.frame(Group = c(rep("SDRev/Iso1", 6), rep("R16/Iso1(REV)", 5)),
                              Count = as.numeric(FC_Points_SDRev[1,]))


points <- bind_rows(
  FC_Points_SDMad,
  FC_Points_SDRev,
  FC_Points_SD5
)

points$Pair <- rep(c("SDMad","SDRev","SD5"),
                   times = c(nrow(FC_Points_SDMad),
                             nrow(FC_Points_SDRev),
                             nrow(FC_Points_SD5)))

points$Pair <- factor(points$Pair, levels=c("SDMad","SDRev","SD5"))
points$Group <- factor(points$Group,
                       levels=c("R16/Iso1(MAD)","SDMad/Iso1",
                                "R16/Iso1(REV)","SDRev/Iso1",
                                "R16/Iso1(SD5)","SD5/Iso1"))

summary_df <- points |>
  dplyr::group_by(Pair, Group) |>
  dplyr::summarise(
    Mean = mean(Count),
    SD = sd(Count),
    .groups="drop"
  )

summary_df$Group <- factor(summary_df$Group,
                           levels = c("R16/Iso1(MAD)","SDMad/Iso1",
                                      "R16/Iso1(REV)","SDRev/Iso1",
                                      "R16/Iso1(SD5)","SD5/Iso1"))

points$Group <- factor(points$Group,
                       levels = levels(summary_df$Group))

summary_Mad <- summary_df[grepl("Mad", summary_df$Pair) == TRUE, ]
summary_Rev <- summary_df[grepl("Rev", summary_df$Pair) == TRUE, ]
summary_5 <- summary_df[grepl("SD5", summary_df$Pair) == TRUE, ]

points_Mad <- points[grepl("Mad", points$Pair) == TRUE, ]
points_Rev <- points[grepl("Rev", points$Pair) == TRUE, ]
points_5 <- points[grepl("SD5", points$Pair) == TRUE, ]

ggplot(summary_Mad, aes(x = Pair, y = Mean, fill = Group)) +
  geom_bar(stat="identity",
           position=position_dodge(width=0.6),
           width=0.6) +
  geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD),
                position=position_dodge(width=0.6),
                width=0.15) +
  geom_point(data=points_Mad,
           aes(x=Pair, y=Count),
           position=position_jitterdodge(
             jitter.width=0.05,
             dodge.width=0.6
           ),
           size=6,
           color="black") +
  scale_fill_manual(values=c("gray","seagreen")) +
  theme_classic() +
  theme(legend.position = "none", axis.text.x = element_text(size = 24), axis.text.y = element_text(size = 15), axis.title.x = element_text(size = 28), axis.title.y = element_text(size = 25))

ggsave("smRNA_CPMPlot_SDMad_Iso1.pdf", width = 8, height = 6, units = c("in"), bg = "transparent")
```

# Supplemental Tables

# Table S2

```{r}
HPsmRNA_SDMadvR16_Iso1 <- SDMad_R16_smRNA_Iso1[SDMad_R16_smRNA_Iso1$Name %in% piRNALoci,1:5]
HPsmRNA_SDMadvR16_Iso1 <- data.frame(Genotype = c(rep("SD-Mad/Iso1", length(HPsmRNA_SDMadvR16_Iso1$Name))), HPsmRNA_SDMadvR16_Iso1)

HPsmRNA_SDMadvR16_Gla <- SDMad_R16_smRNA_Gla[SDMad_R16_smRNA_Gla$Name %in% piRNALoci,1:5]
HPsmRNA_SDMadvR16_Gla <- data.frame(Genotype = c(rep("SD-Mad/Gla", length(HPsmRNA_SDMadvR16_Gla$Name))), HPsmRNA_SDMadvR16_Gla)

HPsmRNA_SD5vR16_Iso1 <- SD5_R16_smRNA_Iso1[SD5_R16_smRNA_Iso1$Name %in% piRNALoci,1:5]
HPsmRNA_SD5vR16_Iso1 <- data.frame(Genotype = c(rep("SD-5/Iso1", length(HPsmRNA_SD5vR16_Iso1$Name))), HPsmRNA_SD5vR16_Iso1)

HPsmRNA_SD5vR16_Gla <- SD5_R16_smRNA_Gla[SD5_R16_smRNA_Gla$Name %in% piRNALoci,1:5]
HPsmRNA_SD5vR16_Gla <- data.frame(Genotype = c(rep("SD-5/Gla", length(HPsmRNA_SD5vR16_Gla$Name))), HPsmRNA_SD5vR16_Gla)

HPsmRNA_SDMadRevvR16_Iso1 <- SDMadRev_R16_smRNA_Iso1[SDMadRev_R16_smRNA_Iso1$Name %in% piRNALoci,1:5]
HPsmRNA_SDMadRevvR16_Iso1 <- data.frame(Genotype = c(rep("SD-MadRev/Iso1", length(HPsmRNA_SDMadRevvR16_Iso1$Name))), HPsmRNA_SDMadRevvR16_Iso1)

HPsmRNA <- rbind(HPsmRNA_SDMadvR16_Iso1, HPsmRNA_SDMadvR16_Gla, HPsmRNA_SD5vR16_Iso1, HPsmRNA_SD5vR16_Gla, HPsmRNA_SDMadRevvR16_Iso1)

write_tsv(HPsmRNA, "supplementalTables/TableS1.tsv")
```

# Table S3

```{r}
HPtotRNA_SDMadvR16_Iso1_Rep <- SDMad_R16_totRNA_Repeats_Iso1[SDMad_R16_totRNA_Repeats_Iso1$Name %in% piRNALoci,1:5]
HPtotRNA_SDMadvR16_Iso1_Rep <- data.frame(Genotype = c(rep("SD-Mad/Iso1", length(HPtotRNA_SDMadvR16_Iso1_Rep$Name))), HPtotRNA_SDMadvR16_Iso1_Rep)

HPtotRNA_SDMadvR16_Gla_Rep <- SDMad_R16_totRNA_Repeats_Gla[SDMad_R16_totRNA_Repeats_Gla$Name %in% piRNALoci,1:5]
HPtotRNA_SDMadvR16_Gla_Rep <- data.frame(Genotype = c(rep("SD-Mad/Iso1", length(HPtotRNA_SDMadvR16_Gla_Rep$Name))), HPtotRNA_SDMadvR16_Gla_Rep)

HPtotRNA_SD5vR16_Iso1_Rep <- SD5_R16_totRNA_Repeats_Iso1[SD5_R16_totRNA_Repeats_Iso1$Name %in% piRNALoci,1:5]
HPtotRNA_SD5vR16_Iso1_Rep <- data.frame(Genotype = c(rep("SD-Mad/Iso1", length(HPtotRNA_SD5vR16_Iso1_Rep$Name))), HPtotRNA_SD5vR16_Iso1_Rep)

HPtotRNA_SD5vR16_Gla_Rep <- SD5_R16_totRNA_Repeats_Gla[SD5_R16_totRNA_Repeats_Gla$Name %in% piRNALoci,1:5]
HPtotRNA_SD5vR16_Gla_Rep <- data.frame(Genotype = c(rep("SD-Mad/Iso1", length(HPtotRNA_SD5vR16_Gla_Rep$Name))), HPtotRNA_SD5vR16_Gla_Rep)

HPtotRNA_Rep <- rbind(HPtotRNA_SDMadvR16_Iso1_Rep, HPtotRNA_SDMadvR16_Gla_Rep, HPtotRNA_SD5vR16_Iso1_Rep, HPtotRNA_SD5vR16_Gla_Rep)

HPtotRNA_Rep <- HPtotRNA_Rep %>% dplyr::arrange(Name)

write_tsv(HPtotRNA_Rep, "supplementalTables/TableS2.tsv")
```



```{r}
HPRspOEvsIso1_SDMad <- SDMad_RspOE_SDMad_smRNA_Iso1[SDMad_RspOE_SDMad_smRNA_Iso1$Name %in% piRNALoci,1:5]
HPRspOEvsIso1_SDMad <- data.frame(Genotype = c(rep("SD-Mad/RspOE", length(HPRspOEvsIso1_SDMad$Name))), HPRspOEvsIso1_SDMad)

HPRspOEdsRed_Iso1_SDMad <- SDMad_RspOE_dsRed_SDMad_smRNA_Iso1[SDMad_RspOE_dsRed_SDMad_smRNA_Iso1$Name %in% piRNALoci,1:5]
HPRspOEdsRed_Iso1_SDMad <- data.frame(Genotype = c(rep("SD-Mad/RspOE-dsRed", length(HPRspOEdsRed_Iso1_SDMad$Name))), HPRspOEdsRed_Iso1_SDMad)

HPRspOEvsIso1_SD5 <- SD5_RspOE_SD5_smRNA_Iso1[SD5_RspOE_SD5_smRNA_Iso1$Name %in% piRNALoci,1:5]
HPRspOEvsIso1_SD5 <- data.frame(Genotype = c(rep("SD-Mad/RspOE", length(HPRspOEvsIso1_SD5$Name))), HPRspOEvsIso1_SD5)

HPRspOEdsRed_Iso1_SD5 <- SD5_RspOE_dsRed_SD5_smRNA_Iso1[SD5_RspOE_dsRed_SD5_smRNA_Iso1$Name %in% piRNALoci,1:5]
HPRspOEdsRed_Iso1_SD5 <- data.frame(Genotype = c(rep("SD-Mad/RspOE-dsRed", length(HPRspOEdsRed_Iso1_SD5$Name))), HPRspOEdsRed_Iso1_SD5)

HPRspOE <- rbind(HPRspOEvsIso1_SDMad, HPRspOEdsRed_Iso1_SDMad, HPRspOEvsIso1_SD5, HPRspOEdsRed_Iso1_SD5)

HPRspOE <- HPRspOE %>% dplyr::arrange(Name)

write_tsv(HPsmRNA, "supplementalTables/TableS4.tsv")
```

